Paper Figures and Text

### 2023-02-16 Fish Data Analysis/Paper_Figures.qmd
Marking place before grouping change
Working on groups in 3D, looking to see how hard it would be to look at all body part distances

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           #filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
                           ungroup()
```

@@

@@

@@

nnd_still
nnd_flow
```
### Height Plot

@@

height_still
height_flow
```

@@

@@

polar_still
polar_flow
```

speed_still
speed_flow
```

area_still
area_flow
```

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB","#FF0000")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB","#FF0000")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

@@

@@

startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
                                             mutate(Exp_Label = "Light") #%>%
                                             #select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val))

>>>>

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed <= 5) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area),
                                  Groups_Mean_Val = mean(Groups), Groups_SD_Val = sd(Groups),
                                  Mean_Groups_Mean_Val = mean(Mean_Groups), Mean_Groups_SD_Val = sd(Mean_Groups),
                                  Height_Mean_Val = mean(School_Height), Height_SD_Val = sd(School_Height)) %>%
                           ungroup()
```

@@

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

@@

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

@@

nnd_still
nnd_flow

nnd_glm <- glm(NND ~ Ablation:Darkness:Flow, data = school_data)
emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness | Flow)

```
### Height Plot

```{r}
my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))

@@

height_still
height_flow

height_glm <- glm(School_Height ~ Ablation:Darkness:Flow, data = school_data)
emmeans(height_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

my_comparisons <- list()

my_comparisons <- list()

polar_still
polar_flow

polar_glm <- glm(School_Polar ~ Ablation:Darkness:Flow, data = school_data)
emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

```{r}
my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))

my_comparisons <- list(c("No Ablation, Light", "Ablated, Light"))

speed_still
speed_flow

speed_glm <- glm(School_Speed ~ Ablation:Darkness:Flow, data = school_data)
emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

area_still
area_flow

area_glm <- glm(Area ~ Ablation:Darkness:Flow, data = school_data)
emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```
### Groups as Mean

mean_group_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Groups,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Groups_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Groups_Mean_Val-Mean_Groups_SD_Val, ymax=Mean_Groups_Mean_Val+Mean_Groups_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Mean Number of Groups") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

mean_group_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Groups,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Groups_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Groups_Mean_Val-Mean_Groups_SD_Val, ymax=Mean_Groups_Mean_Val+Mean_Groups_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Mean Number of Groups") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

mean_group_still
mean_group_flow

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#1D3557","#325A7C","#457B9D","#7BAFBF","#A8DADC","#D0EBE6","#F1FAEE","#e63946")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#1D3557","#325A7C","#457B9D","#7BAFBF","#A8DADC","#D0EBE6","#F1FAEE","#e63946")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

@@

groups_glm <- glm(Groups ~ Ablation:Darkness:Flow, data = school_data)
emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)

@@

startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
                                             mutate(Exp_Label = "Light") %>%
                                             select(-c(Z_SD, Groups, Groups_Mean_Val,Groups_SD_Val,
                                                       School_Height, Height_Mean_Val, Height_SD_Val))
